Ricci-Ollivier Curvature of the Rooted Phylogenetic Subtree-Prune-Regraft Graph\tnoteref{t1,t2}

### 2016-04-22 curvature.tex
fixed overful hbox

rSPR operations give rise to a distance measure between $X$-trees: $\dspr{T_1, T_2}$ is the minimum number of rSPR operations required to transform an $X$-tree $T_1$ into $T_2$.
For example, the trees in Figure~\ref{fig:two-spr} are separated by two rSPR operations.
Moreover, rSPR operations naturally give rise to a graph on the set of $X$-trees for which this distance is simply the shortest-path graph distance.
Let $\mathcal{T}_n$ be the set of trees with $n$ leaves and label set $X = \set{1, 2, \ldots n, \rho}$.
Then the rSPR graph $G$ of $\mathcal{T}_n$ is the graph with vertex set $V(G) = \mathcal{T}_n$ and edge set $E(G) = \set{(T,S) \mid \dspr{T,S} = 1, T \in V, S \in V}$.
Figure~\ref{fig:4-taxa-treespace} illustrates the rSPR graph of 4-leaf trees.

>>>>

rSPR operations induce a distance measure between $X$-trees: $\dspr{T_1, T_2}$ is the minimum number of rSPR operations required to transform an $X$-tree $T_1$ into $T_2$.
For example, the trees in Figure~\ref{fig:two-spr} are separated by two rSPR operations.
Moreover, rSPR operations naturally give rise to a graph on the set of $X$-trees for which this distance is simply the shortest-path graph distance.
Let $\mathcal{T}_n$ be the set of trees with $n$ leaves and label set $X = \set{1, 2, \ldots n, \rho}$.
Then the rSPR graph $G$ of $\mathcal{T}_n$ is the graph with vertex set $V(G) = \mathcal{T}_n$ and edge set $E(G) = \set{(T,S) \mid \dspr{T,S} = 1, T \in V, S \in V}$.
Figure~\ref{fig:4-taxa-treespace} illustrates the rSPR graph of 4-leaf trees.
